% \documentclass[]{ieeeconf} 
\documentclass[letterpaper, 10 pt, conference]{ieeeconf} 
\IEEEoverridecommandlockouts
\overrideIEEEmargins
%\pdfobjcompresslevel=0
%\pdfminorversion=4



% \PassOptionsToPackage{draft}{graphicx} 
\usepackage{graphicx}
\usepackage[hypertexnames=false]{hyperref}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsfonts}
% \usepackage[shortlabels]{enumitem} 

\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{xcolor}
\usepackage{svg}
\let\labelindent\relax
\usepackage{enumitem}
\newenvironment{tightitemize}{%
  \vspace{-0.4em}%
  \begin{itemize}[nosep, topsep=0pt, partopsep=0pt, itemsep=1pt, parsep=0pt, leftmargin=1em]%
}{%
  \end{itemize}%
  % \vspace{-0.5em}%
}

\usepackage{cite}

% \newcommand{\ktxt}[1]{{\color{blue} #1}}
% \newcommand{\ktxt}[1]{}


% Low-Cost Whole-Arm Force-Sensing Skins for Mobile Manipulators
\title{\LARGE \bf Tailorable Force-Sensing Skins for Manipulators Using Textile and Additive Manufacturing
}

% \author{Anonymous authors}
\author{Adam Imdieke$^{1}$, Heidi Woelfle$^{2}$, Brad Holschuh$^{2}$ and Karthik Desingh$^{1}$%
\thanks{$^{1}$Robotics: Perception and Manipulation (RPM) Lab, Department of Computer Science \& Engineering, University of Minnesota, Minneapolis, MN, USA.}%
\thanks{$^{2}$Wearable Technology Lab (WTL), Department of Design Innovation, University of Minnesota, St. Paul, MN, USA.}}

% Add this to set PDF metadata in your root.tex:
\hypersetup{
    pdftitle={Tailorable Force-Sensing Skins for Manipulators Using Textile and Additive Manufacturing},
    pdfauthor={Adam Imdieke, Heidi Woelfle, Brad Holschuh, Karthik Desingh},
    pdfkeywords={tactile sensing, force sensing, robotic manipulation, textile sensors}
}

\begin{document}
\maketitle
\thispagestyle{empty}
\pagestyle{empty}


\begin{abstract}
Robotic manipulation in human-centered and cluttered environments requires not only precise end-effector control but also the ability to sense and regulate contact forces across the entire arm. Restricting tactile sensing to the fingertips or gripper limits a robot's ability to detect, modulate, and safely respond to contact occurring along its links during motion. Whole-arm tactile sensing enables both contact avoidance and deliberate contact exploitation, yet practical tactile skins remain difficult to realize due to trade-offs between fabrication cost, surface coverage, sensing density, usable force range, and long-term repeatability.
We present two complementary whole-arm tactile skin architectures that jointly address this trade-off: a textile-based design configured for lower-force sensitivity and contact avoidance, and a 3D-printed conformal shell configured for higher-threshold contact embracing. Both designs use a resistive taxel matrix and cost under \$10 per link. We provide fabrication guidelines, tunable design parameters, and quantitative characterization of force range, repeatability, and hysteresis. Experiments on a mobile manipulator demonstrate both contact avoidance and controlled contact-embracing behaviors in real-world tasks.
Additional quantitative characterization data and supplementary results are available at the project website: \url{https://rpm-lab-umn.github.io/TactileSkin/}
\end{abstract} 


\input{sections/introduction}
\input{sections/related_works} 
\input{sections/sensor_designs.tex}
\input{sections/sensor_modeling}
\input{sections/sensor_characterization}
\input{sections/results.tex}
\input{sections/conclusion.tex}
\input{sections/acknowledgments.tex}

\bibliographystyle{IEEEtran}
\bibliography{references.bib}

\end{document}
